\documentclass[a4paper]{tufte-handout}

\usepackage{dashrule}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{units}

\title{Imperial College Dramatic Society Constitution}
% \author[The ICDS Committee]{The ICDS Committee}
\date{Proposed revision February 2015}

\newcommand{\policyOffset}{12pt}

\newcommand{\policyCspp}[2][\policyOffset]{\marginnote[#1]{\textsc{CSP Policy \S#2}}}
\newcommand{\policyCspEquip}[2][\policyOffset]{\marginnote[#1]{\textsc{CSP Equipment Policy \S#2}}}
\newcommand{\policyBye}[2][\policyOffset]{\marginnote[#1]{\textsc{Bye-laws \S#2}}}
\newcommand{\policyAE}[2][\policyOffset]{\marginnote[#1]{\textsc{A\&E Standing Orders \S#2}}}
\newcommand{\policyHs}[2][\policyOffset]{\marginnote[#1]{\textsc{Health \& Safety Policy \S#2}}}
\newcommand{\policyPub}[2][\policyOffset]{\marginnote[#1]{\textsc{Publicity Policy \S#2}}}
\newcommand{\policyTankard}[1][\policyOffset]{\marginnote[#1]{\textsc{Tankards Policy}}}

\addtolength{\hoffset}{24pt}

\begin{document}

\maketitle

\begin{fullwidth}
\itshape

\begin{abstract}
This constitution describes the structure of the Imperial College Dramatic Society and the procedures that govern it.
References to relevant sections of the Imperial College Union Constitution, Bye-laws and Policies are indicated alongside the text.
\end{abstract}
\end{fullwidth}

\hdashrule{15cm}{1.1pt}{1.1pt}

\section{Introduction}
\begin{enumerate}
    \item Imperial College Dramatic Society shall be a Society of the Imperial College Union and may hereafter be referred to as `the Society', `ICDS' or `DramSoc'.
    \item \policyCspp{33} The Society shall be a member of the Arts and Entertainments Management Group.
    \item `ICU' or the `Union' refers to Imperial College Union, and `IC' or the `College' refers to Imperial College London.
    \item The `Union Constitution' refers to the Constitution of the Union that is currently in force, as passed by the Union and College Councils and as may be amended from time to time according to \S12 of said Constitution.
    \item The `Union Bye-Laws' or `Bye-laws' shall refer to the \textit{Bye-laws of Imperial College Union} as passed by the Union and College Councils and as may be amended from time to time according to \S11 of the Union Constitution.
    \item The `CSP Policy' shall refer to the \textit{ICU Clubs, Societies and Projects Policy}.
    \item A Full Member of the Union is any Member of the Union that is not an Associate Member.
    \item Written notice, for the purpose of this document, shall be that as defined by \S114 of the Union Constitution.
\end{enumerate}

\section{Objectives}
\begin{enumerate}[resume]
    \item The society aims to:
        \begin{enumerate}
            \item promote the furtherance of drama and the art of theatre in the Imperial College community.
            \item present regular theatrical productions of the highest possible quality.
            \item facilitate interaction with the student drama community outside of Imperial College.
            \item provide support for the development of talent, the encouragement of new writing, and the development of novel and innovative artistic techniques in all fora of theatrical production.
            \item provide technical support for theatrical productions of DramSoc and any other Club, Society or Project of the Arts and Entertainments Management Group.
            \item promote the furtherance of its Members' technical excellence in the fields of design and engineering for theatre and live music.
        \end{enumerate}
    \item The society shall strive to achieve these objectives as its commitment to its membership. 
\end{enumerate}

\section{Membership}
\begin{enumerate}[resume]
    \item Membership of the Society is dichotomised into \textsc{Full Members} of the Society and \textsc{Non-Voting Members} of the Society.
    \item \policyBye{B6} The voting membership of the Society is all of the Full Members of the Society.
    \item \policyCspp{67} Full Members of the Imperial College Union are exclusively able to become Full Members of the Society.
    \item \policyCspp{71} Associate Members of the Union may become Non-Voting Members of the Society.
    \item Sir Walter Plinge is offered honourary Non-Voting Membership of the Society.
    \item \policyCspp{17} Full and Associate Members of the Union may freely join the Society, subject to their paying any fee as may from time-to-time be stipulated by the Committee. If such a fee is charged, it shall be in accordance with any minimum specified in Union Policy.
    \item \policyAE{5.3,} \policyBye{B2} Union Members entitled to \textit{ex officio} membership are Non-Voting Members of the Society, unless they join the Society as a Full Member, satisfying all of the requirements placed thereupon.
\end{enumerate}

\section{Committee}
\begin{enumerate}[resume]
    \item Management of the Society, its funds and its property is vested in the Committee.
    \item The Committee shall have the power to resolve upon regulations and bye-laws as it sees fit, which may be enacted subservient to this constitution.
    \item All officers sitting on the Committee must be Members of the Society.
    \item \policyCspp{66} Any officer holding a voting position on the Committee must be a Full Member of the Society.
    \item No officer may hold more than one position upon the Committee.
    \item \policyCspp{65} The Committee shall consist of thirteen voting officers holding the following positions:
        \begin{enumerate}
            \item President
            \item Vice-President
            \item Treasurer
            \item Honorary Secretary
            \item Acting Director
            \item Technical Director
            \item Lighting Director
            \item Sound Director
            \item Design Director
            \item Pub. Officer
            \item Social Secretary
            \item Systems Administrator
            \item Ordinary Committee Member
        \end{enumerate}
    \item \policyCspp{65} The term of office for all positions runs from the 1st of August to the 31st of July.
    \item A position of office may be vacated by: \begin{enumerate}
            \item Resignation
            \item `RON' being elected at the AGM
            \item Death
        \end{enumerate}
    \item Any officer ceasing to qualify for Full Membership of the Society must resign their position.
    \item \policyBye{G26,} \policyCspp{78} Should an office fall empty, a by-election shall be held at a General Meeting called by the President, which shall be subject to the same regulations as the elections held at the Annual General Meeting.
\end{enumerate}

\subsection{Meetings}
\begin{enumerate}[resume]
    \item Meetings of the Committee shall be called by the President, and shall be held at least monthly.
    \item A meeting must be called by the President upon the request of any three members of the Committee.
    \item The President or their delegated authority shall chair meetings of the Committee.
    \item Meetings of the Committee shall normally be held in the DramSoc Storeroom on Level 2M of the Imperial College Union.
    \item At least five College days' written notice of meetings of the Committee shall be provided by the Secretary to members of the Committee.
    \item Only members of the Committee holding one of the aforementioned voting positions may vote.
    \item \policyBye{B11} Quorum of the Committee shall be 6.
    \item Any Member of the Society may submit to the Secretary a request to attend any Committee Meeting as a guest. This request must be made in writing at least three College Days in advance of the meeting. Such a request shall be considered by the Committee and may only be rejected by vote, and with good reason provided to the guest.
    \item The Committee may invite other Members of the Society, other Members of the Union, or others outside of the Union as guests of the Committee, as it sees fit. 
    \item Guests of the Committee must ask permission from the Chair of the meeting to speak (ordinarily the President).
    \item The Secretary or their delegated authority shall circulate agenda for meetings of the Committee no less than two College days in advance of the meeting, and must publish minutes of that meeting within three College days following the meeting. These minutes must be accepted as a true and accurate record of the previous meeting at the next meeting of the Committee.
    \item A member of the Committee may choose to speak \textit{in camera}, during which minutes shall not be taken and non-members of the Committee must leave.
    \item Committee members must strive to attend all meetings of the Committee, and are obliged to submit apologies to the Secretary if they are unable to do so for whatever reason.
\end{enumerate}

\subsection{Subcommittees}
\begin{enumerate}[resume]
    \item The Committee may create further committees, without derogating from its responsibility, as its members see fit. Such committees shall be sub-committees of the Committee and shall be chaired and constituted as the Committee sees fit.
    \item Such sub-committees shall not have decision making powers binding on the Society, but may make recommendations to the Committee.
    \item Any member of the Committee shall be entitled to sit on any sub-committee.
    \item All members of sub-committees need only to be Members of the Union, not of the Society.
\end{enumerate}

\subsection{Officers}
\begin{enumerate}[resume]
    \item \policyPub{4} The Pub. Officer, Secretary, and Vice President are delegated authority by the President to authorise publicity.
    \item \newthought{The President:}
        \begin{enumerate}
            \item \policyCspp{8} shall be the senior officer of the Society.
            \item shall represent the Society to other societies, the public, external bodies, and any body of the Union (such as the Arts and Entertainments Management Group).
            \item is ultimately responsible for the artistic output of the Society.
            \item \policyCspp{83.i} shall be, along with the Treasurer, financially responsible for the Society.
            \item is responsible for ensuring that the Society is run according to this constitution.
            \item shall possess the casting vote in the event of a tie in a vote at a Committee meeting or General Meeting of the Society.
            \item shall deputise or direct other members of the Committee to deputise for vacant positions, should this become necessary.
            \item shall liaise with the other society (for the purpose of Alumni integration) and the other other society (for the purpose of making a song and dance).
            \item shall be responsible for ensuring that risks arising during the execution of the Society's activities are appropriately identified and mitigated.
            \item \policyHs{26.3.4} shall be responsible for informing the Union of any controls and provisions made to identify and mitigate risks to society Members (to include the annual submission of a risk assessment).
            \item shall be responsible for ensuring that all plays produced by the Society have assigned to them a \textsc{Producer}, who shall be a Member of the Society responsible for the execution of the play (to include its financial aspects), and who shall be answerable to the Committee. This Producer must not also be the show's director.
            \item the authority to authorise publicity may be revoked or further devolved as the President sees fit.
    \end{enumerate}
    \item \newthought{The Vice-President:}
        \begin{enumerate}
            \item shall assist the President in the running of the Society.
            \item shall deputise for the President in their absence.
            \item \policyPub{4} may, at the President's discretion, be delegated authority by the President to authorise publicity.
        \end{enumerate}
    \item \newthought{The Treasurer:}
        \begin{enumerate}
            \item \policyCspp{83.i} shall be, along with the President, financially responsible for the Society.
            \item shall carry out the day-to-day financial duties of the Society.
            \item shall maintain accounts describing the Society's finances, in accordance with accepted accounting rules and practices.
            \item shall maintain accounts for each of the Society's plays, including the allocation of a budget, and recording information about ticket-takings.
            \item shall be responsible for ensuring the long-term financial viability of the Society, by holding reserves or instigating other structural measures as may be necessary to safeguard the objectives of the Society.
            \item shall be responsible for participating in the Union's annual budgeting process.
        \end{enumerate}
    \item \newthought{The Honorary Secretary:}
        \begin{enumerate}
            \item shall be responsible for keeping records of the running of the Society and maintaining its archives in good order.
            \item shall be responsible for communicating announcements to the membership of the Society and the Committee.
            \item shall be responsible for ensuring that all documentation required by the CSP Policy, \S83 are submitted as required.
            \item \policyPub{4} may, at the President's discretion, be delegated authority by the President to authorise publicity.
        \end{enumerate}
    \item \newthought{The Acting Director:}
        \begin{enumerate}
            \item shall have overall responsibility for the Society's thespian activities.
            \item shall have responsibility for the training of Members of the Society in fields relating to acting, to include the organisation of acting workshops.
            \item shall be responsible for ensuring that a Director can be found for the Society's plays, deputising if necessary.
        \end{enumerate}
    \item \newthought{The Technical Director:}
        \begin{enumerate}
            \item shall have overall responsibility for the Society's technical activities.
            \item \policyCspEquip{A3, {\S}A5 \& {\S}B7} shall have overall responsibility for the Society's equipment, including its management and safe usage.
            \item shall ensure that the Society maintains an appropriate level of technical capability, in terms of both equipment and personnel, to enable the Society to achieve its objectives.
            \item shall be responsible for the creation, regular review, and enforcement of a code of practice for technicians covering aspects of safety procedure and working practice, to which all Members of the Society must adhere.
            \item \policyCspEquip{A5.2 \& {\S}A5.3} shall be responsible overall for the training of Members in all aspects of the Society's technical activities.
            \item \policyCspEquip{C} shall ensure that all equipment is maintained and kept securely in good safe working order, and that records are kept of this maintenance and of the equipment owned by the Society.
            \item \policyCspEquip{A7} shall ensure that all equipment and storage is appropriately labelled.
            \item shall be responsible for ensuring that a Production Manager is assigned to all external events, who shall be a Member of the Society answerable to the Committee for that event. An external event is one to which the Society contributes but which the Society does not principally control or fund.
            \item \policyCspEquip{A6} shall ensure that appropriate records are kept and fees are lodged with the Treasurer when equipment is hired.
            \item shall be responsible for the maintenance of the DramSoc Storeroom.
            \item shall be responsible for liaising with the Union over the management, maintenance and upkeep of the Union Concert Hall.
        \end{enumerate}
    \item \newthought{The Lighting Director:}
        \begin{enumerate}
            \item shall have general responsibility for the Society's lighting equipment.
            \item shall be responsible for the maintenance of the Society's lighting equipment.
            \item shall be responsible for advising the Committee on the maintenance of an appropriate level of technical capability in the lighting department.
            \item shall be responsible for the training of other Members of the Society in fields relating to lighting design and engineering.
        \end{enumerate}
    \item \newthought{The Sound Director:}
        \begin{enumerate}
            \item shall have general responsibility for the Society's sound equipment.
            \item shall be responsible for the maintenance of the Society's sound equipment.
            \item shall be responsible for advising the Committee on the maintenance of an appropriate level of technical capability in the sound department.
            \item shall be responsible for the training of other Members of the Society in fields relating to sound design and engineering.
        \end{enumerate}
    \item \newthought{The Design Director:}
        \begin{enumerate}
            \item shall be responsible for the storage and upkeep of the Society's set, costume props.
            \item shall be responsible for the upkeep of the Society's workshop spaces.
            \item shall be responsible for the management and maintenance of all construction tools and instructing Members on their correct and safe use.
            \item shall provide support, guidance and assistance to set, prop and costume designers for the Society's shows.
            \item shall manage the hire of set, costumes and props to other Union bodies and to external parties.
        \end{enumerate} \pagebreak[2]
    \item \newthought{The Pub. Officer:}
        \begin{enumerate}
            \item shall be responsible for ensuring that the Society and its activities are publicised to Members of the College.
            \item shall design, establish, and maintain a coherent consistent brand image for the Society.
            \item shall ensure that publicity is orchestrated for the Society's plays.
            \item shall be responsible for maintaining the content of the Society's website.
            \item shall be responsible for managing the Society's social media accounts.
            \item shall be responsible for the production of society merchandise.
            \item shall ensure that photographs are taken and archived of every society show, along with that show's publicity material.
            \item \policyPub{4} may, at the President's discretion, be delegated authority by the President to authorise publicity.
        \end{enumerate}
    \item \newthought{The Social Secretary:}
        \begin{enumerate}
            \item shall be responsible for the organisation of social events to promote the cohesion and happiness of the Members of the Society.
            \item shall provide compulsory fun.
        \end{enumerate}
    \item \newthought{The Systems Administrator:}
        \begin{enumerate}
            \item shall be responsible for the design, upkeep, security and maintenance of the computer systems and networks utilised in the day-to-day running of the Society, to include:
                \begin{enumerate}
                    \item Routers and switches
                    \item Workstations
                    \item E-Mail accounts
                    \item Mailing lists
                    \item Domains and DNS records
                    \item Printers
                    \item Other information systems as may from time to time become necessary, as directed by the Committee.
                \end{enumerate}
            \item shall assist the Pub. Officer in the maintenance of the website by providing them with the necessary tools to update it.
        \end{enumerate}
    \item \newthought{The Ordinary Committee Member:}
        \begin{enumerate}
            \item shall contribute to the running of the Society in an ordinary fashion, as directed from time to time by the President or the Committee.
        \end{enumerate}
\end{enumerate}

\section{General Meetings}
\begin{enumerate}[resume]
    \item The President may call General Meetings of the Society.
    \item \policyCspp{74} A general meeting must be called by the President at the behest of any one of:
        \begin{enumerate}           
            \item quorum of the Committee, or;
            \item a petition of ten or more Members made to the President in writing.
        \end{enumerate}
    \item General meetings may only be called during undergraduate term time, and must take place on, or in close vicinity of, the South Kensington campus.
    \item A General Meeting may not be called to start after 2100 or before 1200.
    \item No fewer than ten College days' notice of a general meeting must be given in writing to Members of the Society.
    \item Members may submit agenda for discussion at a general meeting to the Secretary no fewer than five College days before a general meeting. Any agendum so submitted must be proposed by a Member and seconded by at least two other Members.
    \item The Secretary must promulgate the agenda for the General meeting to the Members of the Society in writing no fewer than four College days in advance of a general meeting.
    \item The first agendum of any general meeting must be to accept the minutes of the previous general meeting, or to note any corrections as upheld by vote, if necessary.
    \item The Secretary or their delegated authority must record accurate minutes of the General meeting, which must be published in writing to the Members of the Society no greater than three College days subsequent to the meeting.
    \item Any Member of the Society may submit an opinion on any agenda to the Secretary \textit{in absentia}, which must be read out at the meeting by the Secretary in their stead.
    \item All decisions are made exclusively by the voting membership of the Society.
    \item \policyBye{B11} Quorum shall be 50\% + 1 of the full Members of the Society, who must be present in person or by appointed proxy.
\end{enumerate}

\subsection{Annual General Meeting}
\begin{enumerate}[resume]
    \item An Annual General Meeting (AGM) shall be called by the President during the Spring term.
    \item The principal business of the AGM shall be:
        \begin{enumerate}
            \item the presentation by each officer of their report of the preceding year.
            \item \policyCspp{75 \& \S77} the election of the officers of the Society, to be conducted as a `Minor Election' in accordance with {\S}G of the By-laws.
        \end{enumerate}
    \item \policyBye{G2} The Committee shall appoint a Returning Officer for the election.
    \item The Returning Officer:
        \begin{enumerate}
            \item may not stand for election.
            \item may not vote in the election.
            \item must be a Member of the Union.
            \item must open nominations for the election no fewer than five College days in advance of the AGM.
            \item must provide a publicly accessible form for the nomination and seconding of candidates.
            \item must promulgate to all Members of the Society via the Secretary details of the arrangements for balloting, nomination and complaints no fewer than ten College days in advance of the AGM.
        \end{enumerate}
    \item Only voting Members of the Society may cast votes in the election.
    \item Only Members who have been nominated by a Full Member of the Society, and subsequently seconded by two Full Members of the Society, may stand for election.
    \item Candidates may be nominated and seconded at the AGM, so long as the above condition is satisfied.
    \item \policyBye{G14} Manifestos must be provided by all nominees, and may either be:
        \begin{enumerate}
            \item written, and submitted in advance in accordance with a timetable determined by the returning officer, or
            \item spoken, and presented by each nominee at the AGM.
        \end{enumerate}
\end{enumerate}

\section{Tankards}
\begin{enumerate}[resume]
    \item \policyTankard The society must maintain Officer Tankards for the following positions:
        \begin{enumerate}
            \item President
            \item Treasurer
            \item Technical Director
        \end{enumerate}
    \item The society may maintain other tankards, as so resolved upon by the Committee.
\end{enumerate}

\section{Constitution}
\begin{enumerate}[resume]
    \item \policyBye{B6,} \policyCspp{81} This document serves as the constitution for the Imperial College Dramatic Society.
    \item \policyCspp{36} Changes to this constitution may be made solely at a quorate General Meeting of the Society by a $\sfrac{2}{3}$ majority vote of the voting membership of the Society.
    \item This constitution shall be reviewed annually by the Committee.
    \item Any proposal to change this constitution must be made in writing to the Secretary as part of an agendum proposal for the General Meeting in question, who shall subsequently promulgate the proposed change as an addendum to the agendum according to the schedule set out above.
    \item For the avoidance of doubt, since {\S}B16 of the bye-laws requires any electronic vote taken as a consequence of and subsequent to an inquorate meeting to obtain only a simple majority to pass, changes to this constitution cannot be ratified via this mechanism, and nor can any other decision that requires a two-thirds majority.
    \item This constitution is binding on the Society, the Committee, and its members.
    \item This constitution must be published publicly, and provided in full to any Member of the Union who requests it.
    \item All antecedent constitutions are hereby revoked.
\end{enumerate}

\section{Subjugation and Interpretation}
\begin{enumerate}[resume]
    \item This constitution shall be interpreted in accordance with the Law of England and Wales.
    \item The Committee shall be the arbiter in any question regarding the interpretation of this constitution.
    \item This constitution, and the Society, is bound by and defers to all superior bodies of the Union.
    \item The operation of the Society and resolutions of the Committee shall be in accordance with the Union Constitution, Bye-Laws, and all and any resolutions adopted as policy by any superior body, including:
        \begin{enumerate}
            \item The CSP Policy
            \item The Equal Opportunities Policy
            \item \policyCspp{33 \& \S36,} \policyAE{3.2} Any resolutions or standing orders of the Arts and Entertainments Management Group
        \end{enumerate}
    \item Nothing within this constitution shall be taken to conflict with any adopted Union Policy.
    \item If any superior body of the Union adopts or has adopted policy which causes any term of this constitution to be invalidated, the remainder shall continue to be held valid notwithstanding.
\end{enumerate}

\end{document}

% vim: expandtab:ts=4:sw=4
